This is the title [Article v\versionnumber]

### 2022-08-19 manuscript/manuscript.tex

The closed-source Amber simulation engine is used in this tutorial to run the necessary MD simulations.
If no Amber installation is available, the MD can be performed other simulation engines compatible with \software{cpptraj}.
If using GROMACS, we propose to prepare the structures and topologies with AmberTools and converting them using \software{acpype.py}.
In that way, a full Amber topology is available for GIST. 
\todo{ (vah) is it necessary to mention GROMACS specifically? I would remove the previous two lines}
Also note that compressed trajectory formats such as \inlinecode{xtc} might bias the entropy calculation.

>>>>

The closed-source Amber simulation engine is used in this tutorial to run the necessary MD simulations.
If no Amber installation is available, the MD can be performed other simulation engines compatible with \software{cpptraj}.
If using GROMACS, we propose to prepare the structures and topologies with AmberTools and converting them using \software{acpype.py}.

\todo {If the simulation was ran using GROMACS, mdtraj can be used to convert GROMACS topology and trajectory in to an Amber file format.}
\todo {vah: I would remove this mention of GROMACs and replace it with a more generall comment. Or we could test if this actually works...}
In that way, a full Amber topology is available for GIST.

Also note that compressed trajectory formats such as \inlinecode{xtc} might bias the entropy calculation.
